---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nflreadr

<!-- badges: start -->
<!-- [![CRAN status](https://img.shields.io/cran/v/nflreadr?style=flat-square&logo=R&label=CRAN)](https://CRAN.R-project.org/package=nflreadr)  -->
<!-- [![Codecov test coverage](https://img.shields.io/codecov/c/github/nflverse/nflreadr?label=codecov&style=flat-square&logo=codecov)](https://codecov.io/gh/nflverse/nflreadr?branch=main) -->
[![Dev status](https://img.shields.io/github/r-package/v/nflverse/nflreadr/master?label=dev&style=flat-square&logo=github)](https://nflreadr.nflverse.com/)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg?style=flat-square)](https://lifecycle.r-lib.org/articles/stages.html)
[![R build status](https://img.shields.io/github/workflow/status/nflverse/nflreadr/R-CMD-check?label=R%20check&style=flat-square&logo=github)](https://github.com/nflverse/nflreadr/actions)
[![nflverse discord](https://img.shields.io/discord/591914197219016707.svg?color=5865F2&label=nflverse%20discord&logo=discord&logoColor=5865F2&style=flat-square)](https://discord.com/invite/5Er2FBnnQa)

<!-- badges: end -->

nflreadr is a low-level package for downloading data from nflverse repositories. 

## Installation

Install the development version from GitHub with:

```{r eval = FALSE}
install.packages("nflreadr", repos = "https://nflverse.r-universe.dev")

# or use remotes/devtools
# install.packages("remotes")
remotes::install_github("nflverse/nflreadr", ref = "dev")
```

## Usage

The main functions of nflreadr are prefixed with load (?).  

```{r}
tictoc::tic()
x <- load_pbp(1999:2020)
tictoc::toc()
tictoc::tic()
x <- load_pbp(1999:2020,file_type = "rds")
tictoc::toc()
```

The following options help configure default `nflreadr` behaviours. 

```{r eval = FALSE}
options(nflreadr.cache) # one of "memory", "filesystem", or "off"
options(nflreadr.prefer) # one of "qs" or "rds"
```


## Roadmap

This package `must` include:

- Functions for loading: 
    - general `rds_from_url()`, `qs_from_url()`, `parquet_from_url()` `r emo::ji("white_check_mark")`
    - pbp `r emo::ji("white_check_mark")`
    - player_stats (aggregated by week ~~or season~~) `r emo::ji("white_check_mark")`
    - schedules (aka Lee's game data) `r emo::ji("white_check_mark")`
    - rosters `r emo::ji("white_check_mark")`
    - team_stats (aggregated by week ~~or season~~)
    - Next Gen Stats data `r emo::ji("white_check_mark")`
- Document the available package options (currently nflreadr.cache and nflreadr.prefer) somewhere. Maybe in `nflreadr-package.R` created with `use_package_doc()`?
- CRAN (because we want to introduce it as a dependency for other packages)

It would be nice if this package included:

- Memoised/cached data by default `r emo::ji("white_check_mark")`
- ~~Optional parallel processing (?) -> we can do this with `parallel::mclapply()` in combination with `do.call("rbind", ...)` to avoid the `future` and `furrr` dependencies~~ `r emo::ji("cross_mark")` *slower than not-parallel*

Design decisions:

-   depend directly on qs as primary? adds weight but is markedly faster than rds `r emo::ji("white_check_mark")`
-   drop parquet support? heavyweight and slower than qs `r emo::ji("white_check_mark")`
-   use option to configure rather than file_type arg? `r emo::ji("white_check_mark")`

