---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nflreadr

<!-- badges: start -->
<!-- [![CRAN status](https://img.shields.io/cran/v/nflreadr?style=flat-square&logo=R&label=CRAN)](https://CRAN.R-project.org/package=nflreadr)  -->
<!-- [![Codecov test coverage](https://img.shields.io/codecov/c/github/nflverse/nflreadr?label=codecov&style=flat-square&logo=codecov)](https://codecov.io/gh/nflverse/nflreadr?branch=main) -->
[![Dev status](https://img.shields.io/github/r-package/v/nflverse/nflreadr/main?label=dev%20version&style=flat-square&logo=github)](https://nflreadr.nflverse.com/)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg?style=flat-square)](https://lifecycle.r-lib.org/articles/stages.html)
[![R build status](https://img.shields.io/github/workflow/status/nflverse/nflreadr/R-CMD-check?label=R%20check&style=flat-square&logo=github)](https://github.com/nflverse/nflreadr/actions)
[![nflverse discord](https://img.shields.io/discord/591914197219016707.svg?color=5865F2&label=nflverse%20discord&logo=discord&logoColor=5865F2&style=flat-square)](https://discord.com/invite/5Er2FBnnQa)

<!-- badges: end -->

nflreadr is a low-level package for downloading data from nflverse repositories. 

## Installation

Install the development version from GitHub with:

```{r eval = FALSE}
install.packages("nflreadr", repos = "https://nflverse.r-universe.dev")

# or use remotes/devtools
# install.packages("remotes")
remotes::install_github("nflverse/nflreadr", ref = "dev")
```

## Usage

The main functions of `nflreadr` are prefixed with load.  

```{r eval = FALSE}
library(nflreadr)
load_pbp(2020)
```

The following options help configure default `nflreadr` behaviours. 

```{r eval = FALSE}
options(nflreadr.cache) # one of "memory", "filesystem", or "off"
options(nflreadr.prefer) # one of "qs" or "rds"
```

You can also configure `nflreadr` to display progress messages with the `progressr` package, e.g.

```{r eval = FALSE}
progressr::with_progress(load_rosters(seasons = 2010:2020))
 |========             |  40%
```

## Getting help

The best places to get help on this package are:

-   the [nflverse discord](https://discord.com/invite/5Er2FBnnQa) (for both this package as well as anything R/NFL related)
-   opening [an issue](https://github.com/nflverse/nflreadr/issues/new/choose)

## Contributing

Many hands make light work! Here are some ways you can contribute to
this project:

-   You can [open an issue](https://github.com/nflverse/nflreadr/issues/new/choose) if you’d like to request specific data or report a bug/error.

-   If you’d like to contribute code, please check out [the contribution guidelines](https://nflverse.github.io/nflreadr/CONTRIBUTING.html).

## Terms of Use

The R code for this package is released as open source under the [MIT License](https://nflverse.github.io/nflreadr/LICENSE.html). NFL data accessed by this package belong to their respective owners, and are governed by their terms of use.

## Roadmap

This package currently includes:

- Functions for loading: 
    - general `rds_from_url()`, `qs_from_url()`, `parquet_from_url()` `r emo::ji("white_check_mark")`
    - pbp `r emo::ji("white_check_mark")`
    - player_stats (aggregated by week) `r emo::ji("white_check_mark")`
    - schedules (aka Lee's game data) `r emo::ji("white_check_mark")`
    - rosters `r emo::ji("white_check_mark")`
    - Next Gen Stats data `r emo::ji("white_check_mark")`
    - team_stats (aggregated by week) `not yet in nflfastR`
    - fantasy player IDs
    - fantasy latest rankings

and may soon include:

- A hex sticker!
- Data dictionaries and vignettes for all functions (still to-go: schedules, rosters, nextgen stats)
- CRAN-standards/readiness (because we want to introduce it as a dependency for other packages)
